\section{Introduction}

Unmanned aerial vehicles (UAVs) increasingly operate in environments where routing conditions can change during flight. Obstacles may appear or disappear, restricted regions may change, and the route selected at launch may no longer be valid later in the mission. This makes dynamic path planning a central problem for autonomous UAV navigation \cite{ghambari2024survey,johnson2026rcsr}.

Classical graph-search algorithms remain a strong baseline for this problem because they are deterministic, interpretable, and optimal when the graph and edge costs are known. Dijkstra's algorithm, in particular, returns a shortest path when all edge weights are non-negative. However, in a dynamic environment, each obstacle change can invalidate the previous path and require replanning from the UAV's current position. This repeated recomputation is correct but may become expensive as environment size and change frequency increase.

Reinforcement learning (RL) provides a different approach. Rather than recomputing a path through explicit graph search, an RL policy maps observations to movement actions after training. This can potentially reduce deployment-time computation and allow reactive behavior under changing conditions. However, learned policies may be suboptimal, may fail in some scenarios, and do not provide the same optimality guarantees as Dijkstra \cite{mannan2023classical,tu2023uav,guo2023uav}.

Before testing RL's adaptability under dynamic conditions, it is necessary to establish that the trained policy performs reasonably well when the environment does not change at all; a policy that cannot approach optimal performance on a static grid is not a meaningful comparison point once obstacles start moving. We therefore evaluate both methods twice: first on a static 40-scenario benchmark that establishes a baseline for path-cost and compute-time behavior, and then on the paired 50-scenario dynamic benchmark that is this paper's primary contribution.

This paper asks whether a dynamically trained RL policy can match or outperform naive Dijkstra replanning in a controlled UAV grid-routing environment. We compare the two methods on success rate, path cost, and compute time, both when the environment is static and when it changes during flight.

The main contributions are:
\begin{itemize}
    \item a shared 15$\times$15 UAV grid environment with identical movement and dynamic-obstacle rules for both methods;
    \item a static baseline evaluation validating the trained RL policy's path quality and compute-time behavior before dynamic obstacles are introduced;
    \item a naive Dijkstra replanning baseline that recomputes after each dynamic obstacle change;
    \item a dynamically trained RL evaluation on the same 50 scenario IDs and start-goal pairs;
    \item a paired statistical comparison using Wilcoxon signed-rank testing.
\end{itemize}
